---
title: "Estimation"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

## Estimation

### Ex. 1

The dataset teengamb concerns a study of teenage gambling in Britain.
Fit a regression model with the expenditure on gambling as the response
and the sex, status, income and verbal score as predictors.

Present the output

```{r correlation}

data %>% 
  select(gamble, income, verbal, sex, status) %>% 
  cor()


```

```{r}
library(moderndive)

# fit regression model

gamble_model <- lm(gamble ~ sex + income + verbal + status, data = data)

# regression table

get_regression_table(gamble_model)
```

Estimate -\> 22.556 it represents the gamble expenditure when sex,
income, verbal and status are at 0.

```{r}
get_regression_points(gamble_model)
```

(a) What percentage of variation in the response is explained by these
    predictors?

```{r}

get_regression_points(gamble_model) %>% 
  summarize(var_y = var(gamble),
            var_y_hat = var(gamble_hat),
            var_residual = var(residual))

```

(b) Which observation has the largest (positive) residual? Give the case
    number.

```{r}
#24	156.00	0	10.00	4	27	61.748	94.252
  
```

(c) Compute the mean and median of the residuals.
(d) Compute the correlation of the residuals with the fitted values.
(e) Compute the correlation of the residuals with the income.
(f) For all other predictors held constant, what would be the difference
    in predicted expenditure on gambling for a male compared to a female

```{r data, warning=FALSE, message=FALSE}
library(faraway)
library(tidyverse)
library(skimr)

data <- teengamb


```

```{r}

data %>% skim()

```

-   From the description above we can observe that sex, income and
    gamble have NOT normal distributions

-   income and gamble skewed to the right

-   sex categorical - dummy variable

```{r}
data %>% 
  ggplot(aes(x=status, y=gamble)) + 
  geom_point() +
  labs(title = "Relationship of status and gamble") + 
  geom_smooth(method = "lm", se = FALSE)
```

Relationship of Predictors with Gambling expenditure

-   [**Sex**]{.ul} -\> 0 = male, 1= female, less female gambling
    expenditure

-   status -\> socioeconomic status based on parents occupation

-   [**income**]{.ul}

-   [**verbal**]{.ul} -\> inverse (negative relationship)

### Ex. 2

5.  Using the prostate data, plot lpsa against l cavol. Fit the
    regressions of lpsa on lcavol and lcavol on lpsa. Display both
    regression lines on the plot. At what point do the two lines
    intersect
