---
title: "HW2"
author: "MGinorio"
date: "2/12/2022"
output:
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CH 2

## AMARR

#### 2.1

The web site www.playbill.com provides weekly reports on the box office
ticket sales for plays on Broadway in New York. We shall consider the
data for the week October 11--17, 2004 (referred to below as the current
week). The data are in the form of the gross box office results for the
current week and the gross box office results for the previous week
(i.e., October 3--10, 2004). The data, plotted in Figure 2.6 , are
available on the book web site in the file playbill.csv. Fit the
following model to the data:
$$ Y =  \beta_{0}+ \beta_1 \overline{x} + e$$where Y is the gross box
office results for the current week (in \$) and x is the gross box
office results for the previous week (in \$).

Complete the following tasks:

```{r data, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(skimr)

#load data
playbill <- read_csv("https://raw.githubusercontent.com/mgino11/Business_Analytics/main/621-Homeworks/playbill.csv")

playbill %>% skim()


```

```{r}
#stablish relationship using scatter plot

playbill %>% 
  ggplot(aes(x=LastWeek, y=CurrentWeek)) + 
  geom_point() +
  labs(title = "Relationship of Gross Results btw Last and Current Week") + 
  geom_smooth(method = "lm", se = FALSE)


# The se = FALSE argument suppresses standard error uncertainty bars

```

#### EDA

-   CurrentWeek $y$ (gross box office results for the current week)

-   LastWeek $x$ (gross box office results for the previous week)

```{r moderndive, message=FALSE, warning=FALSE}

library(moderndive)

playbill %>% 
  get_correlation(formula = CurrentWeek~LastWeek)
```

```{r}

# fit regression model 
pbill_model <- lm(CurrentWeek~LastWeek, data = playbill )

#Get REgression Table
get_regression_table(pbill_model)

```

```{r}
regression_points <- get_regression_points(pbill_model)
regression_points
```

1.  Find a 95% confidence interval for the slope of the regression
    model, b1.

    Is 1 a plausible value for b1? Give a reason to support your answer.

#### Standard Error Method

2.  Test the null hypothesis 0 0 H : 10000 b = against a two-sided
    alternative. Interpret your result.

3.  Use the fitted regression model to estimate the gross box office
    results for the current week (in \$) for a production with \$400,000
    in gross box office the previous week. Find a 95% prediction
    interval for the gross box office results for the current week (in
    \$) for a production with \$400,000 in gross box office the previous
    week. Is \$450,000 a feasible value for the gross box office results
    in the current week, for a production with \$400,000 in gross box
    office the previous week? Give a reason to support your answer.

4.  Some promoters of Broadway plays use the prediction rule that next
    week's gross box office results will be equal to this week's gross
    box office results. Comment on the appropriateness of this rule.

#### 2.2

```{r packages}


```

## LMR

#### 2.4

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to
prevent printing of the R code that generated the plot.

#### 2.5
